A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
completion time data

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
%\begin{figure*}[h]
%\centering
%\includegraphics[width=7in]{figures/natlang-pie}
%\caption{Self-reported native language of 3,154 bilingual turkers}
%\label{lang-pie}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/completiontime}
\caption{Time (in days) to complete all HITs in each language. Red bar shows time until first HIT was started, relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). Blue bar shows time until all HITs in each language were completed.}
\label{completion-time}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
%\begin{figure*}[h]
%\centering
%\includegraphics[width=7in]{figures/natlang-pie}
%\caption{Self-reported native language of 3,154 bilingual turkers}
%\label{lang-pie}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
